\documentclass[10pt]{article}
    \usepackage[english]{babel}
    \input{config/minimal-resume-config}
    \begin{document}
    
\begin{center}
	% Personal
	% -----------------------------------------------------
	{\fontsize{\sizeone}{\sizeone}\fontspec[Path = fonts/,LetterSpace=15]{Montserrat-Regular} GUILHERME DE ANDRADE}
	\\
	\vspace{2mm}
	{\fontsize{1em}{1em}\fontspec[Path = fonts/]{Montserrat-Light} guilhermedeandrade@proton.me -- +351 936 747 095 -- Porto, Portugal -- github.com/ubmit}
\end{center}
% Chapter: Work Experience
% ------------------------
\chap{EXPERIENCE}{
	
	\job
	{Viz.ai}
	{Feb 2022 – Present}
	{Frontend Engineer}
	{Porto, Portugal}
	{\begin{newitemize}
		\item {Leveraged CSS media queries to add support for smaller screens, significantly enhancing user efficiency.}
		\item {Managed the company\textquotesingle{}s Design System using React, Material UI, styled-components and Storybook.}
		\item {Improved web app security, achieving an A+ grade on SSL Labs’ Server Test.}
		\end{newitemize}}
	\job
	{New Work SE}
	{Nov 2020 – Feb 2022}
	{Frontend Engineer}
	{Porto, Portugal}
	{\begin{newitemize}
		\item {Migrated Embedded Ruby (ERB) templates to React, enhancing the UX on xing.com B2C payments.}
		\item {Maintained an internal NPM package used by multiple teams within the company.}
		\item {Mentored an intern who was hired later on as a Junior Frontend Engineer by New Work SE.}
		\end{newitemize}}
	\job
	{MOXY}
	{Nov 2019 – Nov 2020}
	{Frontend Engineer}
	{Porto, Portugal}
	{\begin{newitemize}
		\item {Developed and maintained websites using React and Next.js, prioritizing UX, code quality, and scalability.}
		\item {Collaborated closely with designers to iterate on products, honing frontend skills, particularly in CSS.}
		\end{newitemize}}
	\job
	{Gistia}
	{Nov 2018 – Nov 2019}
	{Software Engineer}
	{Remote}
	{\begin{newitemize}
		\item {Introduced UI testing using Jest and React Testing Library.}
		\item {Implemented Swagger in our Express.js backend, enhancing the DX and collaboration.}
		\end{newitemize}}
	\job
	{TrackingTrade}
	{Mar 2018 – Jul 2018}
	{Software Engineer Intern}
	{Recife, Brazil}
	{\begin{newitemize}
		\item {Developed and maintained Ruby on Rails applications, particularly dashboards, with AngularJS.}
		\end{newitemize}}
}
% Chapter: Skills
% ------------------------

\chap{SKILLS}{
	\begin{newitemize}
		\item Programming Languages: JavaScript, TypeScript, HTML, CSS, Ruby
		\item Tools \& Technologies: React, Next.js, Remix, Express.js, React Native, Jest, React Testing Library, Tailwind CSS, styled-components, Ruby on Rails, AngularJS, PostgreSQL, MongoDB, GraphQL
		\item Languages: Native Portuguese, Fluent English, Basic German
	\end{newitemize}
}
% Chapter: Education
% ------------------

\chap{EDUCATION}{
	
	\school
	{Faculty of Engineering of the University of Porto (FEUP)}
	{Sep 2018 – Sep 2019}
	{BSc Electrical and Computers Engineering (Incomplete)}
	{Porto, Portugal}
	{
	}
	\school
	{Polytechnic School of Pernambuco (POLI-UPE)}
	{Jan 2016 – Jul 2018}
	{BSc Electronics Engineering (Incomplete)}
	{Recife, Brazil}
	{
	}
}


\ 
\end{document}